---
title: "ParallelCoordinates"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggpubr)
library(GGally)
library(here)
library(tidyverse)
library(tidygraph)
library(network)
library(visNetwork)
library(networkD3)
```
## Demographic Data:
```{r}
cat <- data.table::fread(here::here("data", "DemographicCategories.csv"))
```

## Template Data Analysis:
```{r}
# Load The Data:
dt <- data.table::fread(here::here("data", "CGCS-Template.csv"))
head(dt)
tail(dt)

# Summarising the Data:
summary(dt)
nrow(dt)
ncol(dt)
dt$Source <- as.character(dt$Source)
dt$Target <- as.character(dt$Target)
str(dt$Source)
str(dt$Target)
# Differentiating between channels:
dt01 <- dt %>% filter(dt$eType == 0 | dt$eType == 1) # Communication Channel
nrow(dt01) # 563
dt23 <- dt %>% filter(dt$eType == 2 | dt$eType == 3) # Procurement Channel
nrow(dt23) # 18
dt4 <- dt %>% filter(dt$eType == 4) # Co-authorship Channel
nrow(dt4) # 1
dt5 <- dt %>% filter(dt$eType == 5) # Demographic Channel
nrow(dt5) # 591
dt6 <- dt %>% filter(dt$eType == 6) # Travel Channel
nrow(dt6) # 52
# Analysis of the Communication channel:
glimpse(dt01)
#unique(dt01)
unique(dt01$eType) # 0 1
unique(dt01$SourceLocation) # NA  5  3  4  0
unique(dt01$TargetLocation) # NA  5  0  3  4
unique(dt01$SourceLatitude) # NA
unique(dt01$SourceLongitude) # NA
unique(dt01$TargetLatitude) # NA
unique(dt01$TargetLongitude) # NA
unique(dt01$Source)
unique(dt01$Target)


dt01 <- subset(dt01, select = -c(SourceLatitude, SourceLongitude)) # SOurce and Target Latitude and Longitude columns removed as all Null.
dt01 <- subset(dt01, select = -c(TargetLatitude, TargetLongitude))
dt01 <- subset(dt01, select = -Weight) # Weight removed as all values 1.
colnames(dt01)
any(dt01$Source) == any(dt01$Target) # True
range(dt01$Source) # 27-67
range(dt01$Target) # 0-67
range(dt01$Time) # 86400-27222388

# Analysis of the Demographic channel:
glimpse(dt5)
#unique(dt5)
unique(dt5$eType) # 5
unique(dt5$SourceLocation) # NA
unique(dt5$TargetLocation) # NA 
unique(dt5$SourceLatitude) # NA
unique(dt5$SourceLongitude) # NA
unique(dt5$TargetLatitude) # NA
unique(dt5$TargetLongitude) # NA
unique(dt5$Source) 
unique(dt5$Target)
unique(dt5$Weight)

dt5 <- subset(dt5, select = -c(SourceLocation, TargetLocation, SourceLatitude, SourceLongitude, TargetLatitude, TargetLongitude)) # SOurce and Target Latitude and Longitude columns removed as all Null.
colnames(dt5)
#any(dt5$Source) == any(dt5$Target) # True
range(dt5$Source) # 0-620120
range(dt5$Target) # 0-644226
range(dt5$Time) # 31536000-31536000
income_cat <- subset(dt5$Source, dt5$Source >= 500000)
unique(income_cat) #Income Categories: 510031(Gifts), 552988(Money Income before Taxes), 620120(Personal Taxes)
expense_cat <- subset(dt5$Target, dt5$Target >= 500000)
sort(unique(expense_cat)) # Expense Categories: 503218(Natural Gas) 503701(Miscellaneous) 520660(Healthcare) 523927(Restaurants) 527449 (Alcohol) 
                                  # 536346(Home Maintenance) 537281(HouseKeeping) 567195 (Personal insurance and pensions) 
                                  # 571970(Reading) 575030 (Transportation) 577992 (Education) 580426 (Telephone services) 
                                  # 589943(Lodging away from home) 595298(Groceries) 595581(Donations) 606730(Entertainment)
                                  # 616315(Apparel and services) 620120(Personal taxes) 621924(Mortgage payments) 
                                  # 630626(Rented dwellings) 632961(Personal care products and services) 
                                  # 640784(Tobacco) 642329(Household operations) 644226(Property taxes)

hist(dt5$Weight)
unique(dt5$Weight)
range(dt5$Weight) #2-200000

# Income Categories:
dt5_sub1 <- subset(dt5, dt5$Source >= 500000) # Subset of data with only income categories
str(dt5_sub1)
plot(dt5_sub1$Source, dt5_sub1$Weight) # Plot of Monetary income in each category

# Expense Categories:
dt5_sub2 <- subset(dt5, dt5$Target >= 500000) # Subset of data with only expense categories
str(dt5_sub2)
plot(dt5_sub2$Target, dt5_sub2$Weight) # Plot of Monetary expenses in each category

#any(dt6$Source) == any(dt6$Target)


```
## Graph 1 Analysis:
```{r}
qt1 <- data.table::fread(here::here("data", "Q1-Graph1.csv"))
head(qt1)
tail(qt1)

# Summarising the Data:
summary(qt1)
nrow(qt1) #1216
ncol(qt1) #11
qt1$Source <- as.character(qt1$Source)
qt1$Target <- as.character(qt1$Target)

# Differentiating between channels:
qt1_01 <- qt1 %>% filter(qt1$eType == 0 | qt1$eType == 1) # Communication Channel
nrow(qt1_01) # 318
qt1_23 <- qt1 %>% filter(qt1$eType == 2 | qt1$eType == 3) # Procurement Channel
nrow(qt1_23) # 14
qt1_4 <- qt1 %>% filter(qt1$eType == 4) # Co-authorship Channel
nrow(qt1_4) # 1
qt1_5 <- qt1 %>% filter(qt1$eType == 5) # Demographic Channel
nrow(qt1_5) # 846
qt1_6 <- qt1 %>% filter(qt1$eType == 6) # Travel Channel
nrow(qt1_6) # 37
# Highest data for Demographic, Communication and Travel Channel.


# Analysis of the Communication channel:
glimpse(qt1_01)
#unique(qt1_01)
unique(qt1_01$eType) # 0 1
unique(qt1_01$SourceLocation) # NA 0 2 3
unique(qt1_01$TargetLocation) # NA 0 2 3
unique(qt1_01$SourceLatitude) # NA  34.5741  34.2958 -27.2563  29.3296 -20.9062 -21.8004  25.0754 -25.4639 -24.5657 -18.3758  30.4483  35.8806
unique(qt1_01$SourceLongitude) # NA  -42.0541  -39.0260   91.7676  -37.8076   92.3982   89.7045  -40.6293 -111.2490 -110.6500   91.0250  -42.5341  -34.5372
unique(qt1_01$TargetLatitude) # NA  30.4483  29.3296  34.2958  34.5741  28.3004 -27.2563 -22.6503 -21.8004 -20.9062  25.0754 -24.5657 -20.8686 -18.3758
                                  # 32.6654 -25.4639 -17.1099  35.8806
unique(qt1_01$TargetLongitude) # NA  -42.5341  -37.8076  -39.0260  -42.0541  -47.4036   91.7676   92.6106   89.7045   92.3982  -40.6293 -110.6500   89.4217
                                        #91.0250  -48.6701 -111.2490   90.7971  -34.5372
unique(qt1_01$Source) # 599956 490041 533140 568093 632150 635665 616050 512397 623295 589639 550287 550361 596193
                          # 464459 492777 570411 640464
unique(qt1_01$Target) # 635665 490041 599956 589639 591682 616050 568093 632150 464459 533140 512397 550287 559657
                            # 492777 570411 493044 596193 550361 640464 623295
qt1_01 <- subset(qt1_01, select = -c(SourceLatitude, SourceLongitude)) # SOurce and Target Latitude and Longitude columns removed as all Null.
qt1_01 <- subset(qt1_01, select = -c(TargetLatitude, TargetLongitude))
qt1_01 <- subset(qt1_01, select = -Weight) # Weight removed as all values 1.
colnames(qt1_01)


# Analysis of the Demographic channel:
glimpse(qt1_5)
#unique(qt1_5)
unique(qt1_5$eType) # 5
unique(qt1_5$SourceLocation) # NA
unique(qt1_5$TargetLocation) # NA
unique(qt1_5$SourceLatitude) # NA
unique(qt1_5$SourceLongitude) # NA
unique(qt1_5$TargetLatitude) # NA
unique(qt1_5$TargetLongitude) # NA
unique(qt1_5$Source)
unique(qt1_5$Target)
unique(qt1_5$Weight)


qt1_5 <- subset(qt1_5, select = -c(SourceLocation, TargetLocation, SourceLatitude, SourceLongitude, TargetLatitude, TargetLongitude)) # SOurce and Target Latitude and Longitude columns removed as all Null.
colnames(qt1_5)


range(qt1_5$Source) # 463777-654981
range(qt1_5$Target) # 459381-654981
range(qt1_5$Time) # 31536000-31536000
income_cat_qt1 <- NULL
# Income Categories:
for (i in (qt1_5$Source)) {
  for (j in (cat$NodeID)) {                   # cat_list contains all the demographic nodeIDs (from the DemographicNodeExtraction Script)
    if(i == j){
      income_cat_qt1 <- append(income_cat_qt1,i)
    }
  }
}

print(income_cat_qt1) # income categories extracted
unique(income_cat_qt1) # 3
qt1_5_sub1 <- subset(qt1_5, qt1_5$Source == income_cat_qt1) # Subset of data with only income categories
str(qt1_5_sub1)
plot(qt1_5_sub1$Source, qt1_5_sub1$Weight) # Plot of Monetary income in each category

# Expense Categories:
expense_cat_qt1 <- 0
for (k in qt1_5$Target) {
  for(l in cat$NodeID){ 
    if(k==l){
      expense_cat_qt1 <- append(expense_cat_qt1, k)
    }
  }

}
print(expense_cat_qt1) # expense categories extracted
unique(expense_cat_qt1) # 27
qt1_5_sub2 <- subset(qt1_5, qt1_5$Target == expense_cat_qt1) # Subset of data with only expense categories
str(qt1_5_sub2)
plot(qt1_5_sub2$Target, qt1_5_sub2$Weight) # Plot of Monetary expenses in each category


hist(qt1_5$Weight)
unique(qt1_5$Weight)
range(qt1_5$Weight) #0.46-900735.00
# To-do : normalise the weights to better visualise in graph. Convert to csv maybe.

```


## Graph 2 Analysis:
```{r}
qt2 <- data.table::fread(here::here("data", "Q1-Graph2.csv"))
head(qt2)
tail(qt2)

# Summarising the Data:
summary(qt2)
nrow(qt2) #1300
ncol(qt2) #11
qt2$Source <- as.character(qt2$Source)
qt2$Target <- as.character(qt2$Target)

# Differentiating between channels:
qt2_01 <- qt2 %>% filter(qt2$eType == 0 | qt2$eType == 1) # Communication Channel
nrow(qt2_01) # 435
qt2_23 <- qt2 %>% filter(qt2$eType == 2 | qt2$eType == 3) # Procurement Channel
nrow(qt2_23) # 14
qt2_4 <- qt2 %>% filter(qt2$eType == 4) # Co-authorship Channel
nrow(qt2_4) # 4
qt2_5 <- qt2 %>% filter(qt2$eType == 5) # Demographic Channel
nrow(qt2_5) # 823
qt2_6 <- qt2 %>% filter(qt2$eType == 6) # Travel Channel
nrow(qt2_6) # 24
# Highest data for Demographic, Communication and Travel Channel.

# Analysis of the Communication channel:
glimpse(qt2_01)
#unique(qt2_01)
unique(qt2_01$eType) # 0 1
unique(qt2_01$SourceLocation) 
unique(qt2_01$TargetLocation) 
unique(qt2_01$SourceLatitude) 
unique(qt2_01$SourceLongitude) 
unique(qt2_01$TargetLatitude) 
unique(qt2_01$TargetLongitude) 
unique(qt2_01$Source) 
unique(qt2_01$Target) 

qt2_01 <- subset(qt2_01, select = -c(SourceLatitude, SourceLongitude)) # SOurce and Target Latitude and Longitude columns removed as all Null.
qt2_01 <- subset(qt2_01, select = -c(TargetLatitude, TargetLongitude))
qt2_01 <- subset(qt2_01, select = -Weight) # Weight removed as all values 1.
colnames(qt2_01)

# Analysis of the Demographic channel:
glimpse(qt2_5)
#unique(qt2_5)
unique(qt2_5$eType) # 5
unique(qt2_5$SourceLocation) # NA
unique(qt2_5$TargetLocation) # NA
unique(qt2_5$SourceLatitude) # NA
unique(qt2_5$SourceLongitude) # NA
unique(qt2_5$TargetLatitude) # NA
unique(qt2_5$TargetLongitude) # NA
unique(qt2_5$Source)
unique(qt2_5$Target)
unique(qt2_5$Weight)


qt2_5 <- subset(qt2_5, select = -c(SourceLocation, TargetLocation, SourceLatitude, SourceLongitude, TargetLatitude, TargetLongitude)) # SOurce and Target Latitude and Longitude columns removed as all Null.
colnames(qt2_5)
any(qt2_5$Source) == any(qt2_5$Target) # True
range(qt2_5$Source) # 464563-656156
range(qt2_5$Target) # 459381-656156
range(qt2_5$Time) # 31536000-31536000
income_cat_qt2 <- NULL
# Income Categories:
for (i in (qt2_5$Source)) {
  for (j in (cat$NodeID)) {                   # cat_list contains all the demographic nodeIDs (from the DemographicNodeExtraction Script)
    if(i == j){
      income_cat_qt2 <- append(income_cat_qt2,i)
    }
  }
}

print(income_cat_qt2) # income categories extracted
unique(income_cat_qt2) # 3
qt2_5_sub1 <- subset(qt2_5, qt2_5$Source == income_cat_qt2) # Subset of data with only income categories
str(qt2_5_sub1)
plot(qt2_5_sub1$Source, qt2_5_sub1$Weight) # Plot of Monetary income in each category

# Expense Categories:
expense_cat_qt2 <- NULL
for (k in qt2_5$Target) {
  for(l in cat$NodeID){ 
    if(k==l){
      expense_cat_qt2 <- append(expense_cat_qt2, k)
    }
  }
  
}
print(expense_cat_qt2) # expense categories extracted
unique(expense_cat_qt2) # 27
qt2_5_sub2 <- subset(qt2_5, qt2_5$Target == expense_cat_qt2) # Subset of data with only expense categories
str(qt2_5_sub2)
plot(qt2_5_sub2$Target, qt2_5_sub2$Weight) # Plot of Monetary expenses in each category


hist(qt2_5$Weight)
unique(qt2_5$Weight)
range(qt2_5$Weight) #0.17-196567.00
# To-do : normalise the weights to better visualise in graph. Convert to csv maybe.

#any(qt2_6$Target) == any(qt2_6$Source)

```



## Graph 3 Analysis:
```{r}
library(here)
library(tidyverse)

# Load The Data:
qt3 <- data.table::fread(here::here("data", "Q1-Graph3.csv"))
head(qt3)
tail(qt3)

# Summarising the Data:
summary(qt3)
nrow(qt3) #729
ncol(qt3) #11
qt3$Source <- as.character(qt3$Source)
qt3$Target <- as.character(qt3$Target)

# Differentiating between channels:
qt3_01 <- qt3 %>% filter(qt3$eType == 0 | qt3$eType == 1) # Communication Channel
nrow(qt3_01) # 160
qt3_23 <- qt3 %>% filter(qt3$eType == 2 | qt3$eType == 3) # Procurement Channel
nrow(qt3_23) # 12
qt3_4 <- qt3 %>% filter(qt3$eType == 4) # Co-authorship Channel
nrow(qt3_4) # 1
qt3_5 <- qt3 %>% filter(qt3$eType == 5) # Demographic Channel
nrow(qt3_5) # 519
qt3_6 <- qt3 %>% filter(qt3$eType == 6) # Travel Channel
nrow(qt3_6) # 37
# Highest data for Demographic, Communication and Travel Channel.

# Analysis of the Communication channel:
glimpse(qt3_01)
#unique(qt3_01)
unique(qt3_01$eType) # 0 1
unique(qt3_01$SourceLocation) # 1  2 NA  4  5  0
unique(qt3_01$TargetLocation) # 2 NA  1  0  4  5
unique(qt3_01$SourceLatitude) # -27.78420 -23.59530 NA -29.17140   5.91178  24.98310  32.11920   2.35166
unique(qt3_01$SourceLongitude)# -8.74823 91.35710 NA -10.49300 -161.27600  155.44600  -47.35310 -161.32200 
unique(qt3_01$TargetLatitude) # -21.89600 -21.14110        NA -29.17140 -27.78420 -23.59530  33.57410   2.35166  32.11920  24.98310 5.91178
unique(qt3_01$TargetLongitude) #  89.40000   91.14270         NA  -10.49300   -8.74823   91.35710  -40.39040 -161.32200  -47.35310 155.44600 -161.27600
unique(qt3_01$Source) 
unique(qt3_01$Target) 

qt3_01 <- subset(qt3_01, select = -c(SourceLatitude, SourceLongitude)) # SOurce and Target Latitude and Longitude columns removed as all Null.
qt3_01 <- subset(qt3_01, select = -c(TargetLatitude, TargetLongitude))
qt3_01 <- subset(qt3_01, select = -Weight) # Weight removed as all values 1.
colnames(qt3_01)

# Analysis of the Demographic channel:
glimpse(qt3_5)
#unique(qt3_5)
unique(qt3_5$eType) # 5
unique(qt3_5$SourceLocation) # NA
unique(qt3_5$TargetLocation) # NA
unique(qt3_5$SourceLatitude) # NA
unique(qt3_5$SourceLongitude) # NA
unique(qt3_5$TargetLatitude) # NA
unique(qt3_5$TargetLongitude) # NA
unique(qt3_5$Source)
unique(qt3_5$Target)
unique(qt3_5$Weight)


qt3_5 <- subset(qt3_5, select = -c(SourceLocation, TargetLocation, SourceLatitude, SourceLongitude, TargetLatitude, TargetLongitude)) # SOurce and Target Latitude and Longitude columns removed as all Null.
colnames(qt3_5)


range(qt3_5$Source) # 466976 657076
range(qt3_5$Target) # 459381 657076
range(qt3_5$Time) # 31536000-31536000
income_cat_qt3 <- NULL
# Income Categories:
for (i in (qt3_5$Source)) {
  for (j in (cat$NodeID)) {                   # cat_list contains all the demographic nodeIDs (from the DemographicNodeExtraction Script)
    if(i == j){
      income_cat_qt3 <- append(income_cat_qt3,i)
    }
  }
}

print(income_cat_qt3) # income categories extracted
unique(income_cat_qt3) # 3
qt3_5_sub1 <- subset(qt3_5, qt3_5$Source == income_cat_qt3) # Subset of data with only income categories
str(qt3_5_sub1)
plot(qt3_5_sub1$Source, qt3_5_sub1$Weight) # Plot of Monetary income in each category

# Expense Categories:
expense_cat_qt3 <- NULL
for (k in qt3_5$Target) {
  for(l in cat$NodeID){ 
    if(k==l){
      expense_cat_qt3 <- append(expense_cat_qt3, k)
    }
  }
  
}
print(expense_cat_qt3) # expense categories extracted
unique(expense_cat_qt3) # 27
qt3_5_sub2 <- subset(qt3_5, qt3_5$Target == expense_cat_qt3) # Subset of data with only expense categories
str(qt3_5_sub2)
plot(qt3_5_sub2$Target, qt3_5_sub2$Weight) # Plot of Monetary expenses in each category


hist(qt3_5$Weight)
unique(qt3_5$Weight)
range(qt3_5$Weight) #1.53 159997.00
# To-do : normalise the weights to better visualise in graph. Convert to csv maybe.



```
## Graph 4 Analysis:
```{r}
# Load The Data:
qt4 <- data.table::fread(here::here("data", "Q1-Graph4.csv"))
head(qt4)
tail(qt4)

# Summarising the Data:
summary(qt4)
nrow(qt4) #732
ncol(qt4) #11
qt4$Source <- as.character(qt4$Source)
qt4$Target <- as.character(qt4$Target)

# Differentiating between channels:
qt4_01 <- qt4 %>% filter(qt4$eType == 0 | qt4$eType == 1) # Communication Channel
nrow(qt4_01) # 106
qt4_23 <- qt4 %>% filter(qt4$eType == 2 | qt4$eType == 3) # Procurement Channel
nrow(qt4_23) # 17
qt4_4 <- qt4 %>% filter(qt4$eType == 4) # Co-authorship Channel
nrow(qt4_4) # 0
qt4_5 <- qt4 %>% filter(qt4$eType == 5) # Demographic Channel
nrow(qt4_5) # 494
qt4_6 <- qt4 %>% filter(qt4$eType == 6) # Travel Channel
nrow(qt4_6) # 115
# Highest data for Demographic, Communication and Travel Channel.

# Analysis of the Communication channel:
glimpse(qt4_01)
#unique(qt4_01)
unique(qt4_01$eType) # 0 1
unique(qt4_01$SourceLocation) # 4  0 NA  5  1  3
unique(qt4_01$TargetLocation) # 4  3 NA  5  2  1  0
unique(qt4_01$SourceLatitude) 
unique(qt4_01$SourceLongitude)
unique(qt4_01$TargetLatitude) 
unique(qt4_01$TargetLongitude) 
unique(qt4_01$Source) 
unique(qt4_01$Target) 

qt4_01 <- subset(qt4_01, select = -c(SourceLatitude, SourceLongitude)) # SOurce and Target Latitude and Longitude columns removed as all Null.
qt4_01 <- subset(qt4_01, select = -c(TargetLatitude, TargetLongitude))
qt4_01 <- subset(qt4_01, select = -Weight) # Weight removed as all values 1.
colnames(qt4_01)

# Analysis of the Demographic channel:
glimpse(qt4_5)
#unique(qt4_5)
unique(qt4_5$eType) # 5
unique(qt4_5$SourceLocation) # NA
unique(qt4_5$TargetLocation) # NA
unique(qt4_5$SourceLatitude) # NA
unique(qt4_5$SourceLongitude) # NA
unique(qt4_5$TargetLatitude) # NA
unique(qt4_5$TargetLongitude) # NA
unique(qt4_5$Source)
unique(qt4_5$Target)
unique(qt4_5$Weight)


qt4_5 <- subset(qt4_5, select = -c(SourceLocation, TargetLocation, SourceLatitude, SourceLongitude, TargetLatitude, TargetLongitude)) # SOurce and Target Latitude and Longitude columns removed as all Null.
colnames(qt4_5)


range(qt4_5$Source) # 466976 657076
range(qt4_5$Target) # 459381 657076
range(qt4_5$Time) # 31536000-31536000
income_cat_qt4 <- NULL
# Income Categories:
for (i in (qt4_5$Source)) {
  for (j in (cat$NodeID)) {                   # cat_list contains all the demographic nodeIDs (from the DemographicNodeExtraction Script)
    if(i == j){
      income_cat_qt4 <- append(income_cat_qt4,i)
    }
  }
}

print(income_cat_qt4) # income categories extracted
unique(income_cat_qt4) # 3
qt4_5_sub1 <- subset(qt4_5, qt4_5$Source == income_cat_qt4) # Subset of data with only income categories
str(qt4_5_sub1)
plot(qt4_5_sub1$Source, qt4_5_sub1$Weight) # Plot of Monetary income in each category

# Expense Categories:
expense_cat_qt4 <- NULL
for (k in qt4_5$Target) {
  for(l in cat$NodeID){ 
    if(k==l){
      expense_cat_qt4 <- append(expense_cat_qt4, k)
    }
  }
  
}
print(expense_cat_qt4) # expense categories extracted
unique(expense_cat_qt4) # 27
qt4_5_sub2 <- subset(qt4_5, qt4_5$Target == expense_cat_qt4) # Subset of data with only expense categories
str(qt4_5_sub2)
plot(qt4_5_sub2$Target, qt4_5_sub2$Weight) # Plot of Monetary expenses in each category


hist(qt4_5$Weight)
unique(qt4_5$Weight)
range(qt4_5$Weight) #2.39 141744.00
# To-do : normalise the weights to better visualise in graph. Convert to csv maybe.



```
## Graph 5 Analysis:
```{r}
# Load The Data:
qt5 <- data.table::fread(here::here("data", "Q1-Graph5.csv"))
head(qt5)
tail(qt5)

# Summarising the Data:
summary(qt5)
nrow(qt5) #395
ncol(qt5) #11
qt5$Source <- as.character(qt5$Source)
qt5$Target <- as.character(qt5$Target)

# Differentiating between channels:
qt5_01 <- qt5 %>% filter(qt5$eType == 0 | qt5$eType == 1) # Communication Channel
nrow(qt5_01) # 31
qt5_23 <- qt5 %>% filter(qt5$eType == 2 | qt5$eType == 3) # Procurement Channel
nrow(qt5_23) # 51
qt5_4 <- qt5 %>% filter(qt5$eType == 4) # Co-authorship Channel
nrow(qt5_4) # 0
qt5_5 <- qt5 %>% filter(qt5$eType == 5) # Demographic Channel
nrow(qt5_5) # 203
qt5_6 <- qt5 %>% filter(qt5$eType == 6) # Travel Channel
nrow(qt5_6) # 110
# Highest data for Demographic, Travel Channel and Procurement.

# Analysis of the Communication channel:
glimpse(qt5_01)
#unique(qt5_01)
unique(qt5_01$eType) # 0 1
unique(qt5_01$SourceLocation) # NA  2  0  4  3
unique(qt5_01$TargetLocation) # NA  4  3  1  5
unique(qt5_01$SourceLatitude) 
unique(qt5_01$SourceLongitude)
unique(qt5_01$TargetLatitude) 
unique(qt5_01$TargetLongitude) 
unique(qt5_01$Source) 
unique(qt5_01$Target) 

qt5_01 <- subset(qt5_01, select = -c(SourceLatitude, SourceLongitude)) # SOurce and Target Latitude and Longitude columns removed as all Null.
qt5_01 <- subset(qt5_01, select = -c(TargetLatitude, TargetLongitude))
qt5_01 <- subset(qt5_01, select = -Weight) # Weight removed as all values 1.
colnames(qt5_01)

# Analysis of the Demographic channel:
glimpse(qt5_5)
#unique(qt5_5)
unique(qt5_5$eType) # 5
unique(qt5_5$SourceLocation) # NA
unique(qt5_5$TargetLocation) # NA
unique(qt5_5$SourceLatitude) # NA
unique(qt5_5$SourceLongitude) # NA
unique(qt5_5$TargetLatitude) # NA
unique(qt5_5$TargetLongitude) # NA
unique(qt5_5$Source)
unique(qt5_5$Target)
unique(qt5_5$Weight)


qt5_5 <- subset(qt5_5, select = -c(SourceLocation, TargetLocation, SourceLatitude, SourceLongitude, TargetLatitude, TargetLongitude)) # SOurce and Target Latitude and Longitude columns removed as all Null.
colnames(qt5_5)


range(qt5_5$Source) # 466976 657076
range(qt5_5$Target) # 459381 657076
range(qt5_5$Time) # 31536000-31536000
income_cat_qt5 <- NULL
# Income Categories:
for (i in (qt5_5$Source)) {
  for (j in (cat$NodeID)) {                   # cat_list contains all the demographic nodeIDs (from the DemographicNodeExtraction Script)
    if(i == j){
      income_cat_qt5 <- append(income_cat_qt5,i)
    }
  }
}

print(income_cat_qt5) # income categories extracted
unique(income_cat_qt5) # 3
qt5_5_sub1 <- subset(qt5_5, qt5_5$Source == income_cat_qt5) # Subset of data with only income categories
str(qt5_5_sub1)
plot(qt5_5_sub1$Source, qt5_5_sub1$Weight) # Plot of Monetary income in each category

# Expense Categories:
expense_cat_qt5 <- NULL
for (k in qt5_5$Target) {
  for(l in cat$NodeID){ 
    if(k==l){
      expense_cat_qt5 <- append(expense_cat_qt5, k)
    }
  }
  
}
print(expense_cat_qt5) # expense categories extracted
unique(expense_cat_qt5) # 27
qt5_5_sub2 <- subset(qt5_5, qt5_5$Target == expense_cat_qt5) # Subset of data with only expense categories
str(qt5_5_sub2)
plot(qt5_5_sub2$Target, qt5_5_sub2$Weight) # Plot of Monetary expenses in each category


hist(qt5_5$Weight)
unique(qt5_5$Weight)
range(qt5_5$Weight) #0.17 441206.00
# To-do : normalise the weights to better visualise in graph. Convert to csv maybe.





```



## Parallel Coordinates for Template and Graph Data:

```{r}
colnames(dt)
ggparcoord(dt, columns = c(1,3,4,5), groupColumn = 4) # Parallel Coords for the Template
ggparcoord(qt1, columns = c(1,3,4,5), groupColumn = 4) # Parallel Coords for Graph 1
ggparcoord(qt2, columns = c(1,3,4,5), groupColumn = 4) # Parallel Coords for Graph 2
ggparcoord(qt3, columns = c(1,3,4,5), groupColumn = 4) # Parallel Coords for Graph 3
ggparcoord(qt4, columns = c(1,3,4,5), groupColumn = 4) # Parallel Coords for Graph 4
ggparcoord(qt5, columns = c(1,3,4,5), groupColumn = 4) # Parallel Coords for Graph 5

```



## Communication Channel:

```{r}
colnames(dt01)
com_temp <- ggparcoord(dt01,columns = c(1,3,4), groupColumn = 4)
com_g1<- ggparcoord(qt1_01,columns = c(1,3,4), groupColumn = 4)
com_g2 <- ggparcoord(qt2_01,columns = c(1,3,4), groupColumn = 4)
com_g3 <- ggparcoord(qt3_01,columns = c(1,3,4), groupColumn = 4)
com_g4 <- ggparcoord(qt4_01,columns = c(1,3,4), groupColumn = 4)
com_g5 <- ggparcoord(qt5_01,columns = c(1,3,4), groupColumn = 4)
ggarrange(com_temp, com_g1, labels = c("Template", "Graph 1"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(com_temp, com_g2, labels = c("Template", "Graph 2"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(com_temp, com_g3, labels = c("Template", "Graph 3"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(com_temp, com_g4, labels = c("Template", "Graph 4"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(com_temp, com_g5, labels = c("Template", "Graph 5"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))

```



## Demographic Channel:

```{r}
dem_temp <- ggparcoord(dt5, columns = c(1,3,4,5),groupColumn = 4)
dem_g1<- ggparcoord(qt1_5,columns = c(1,3,4,5), groupColumn = 4)
dem_g2 <- ggparcoord(qt2_5,columns = c(1,3,4,5), groupColumn = 4)
dem_g3 <- ggparcoord(qt3_5,columns = c(1,3,4,5), groupColumn = 4)
dem_g4 <- ggparcoord(qt4_5,columns = c(1,3,4,5), groupColumn = 4)
dem_g5 <- ggparcoord(qt5_5,columns = c(1,3,4,5), groupColumn = 4)
ggarrange(dem_temp, dem_g1, labels = c("Template", "Graph 1"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(dem_temp, dem_g2, labels = c("Template", "Graph 2"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(dem_temp, dem_g3, labels = c("Template", "Graph 3"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(dem_temp, dem_g4, labels = c("Template", "Graph 4"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(dem_temp, dem_g5, labels = c("Template", "Graph 5"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
```


## Travel Channel:

```{r}
tra_temp <- ggparcoord(dt6, columns = c(1,3,4,5),groupColumn = 4)
tra_g1<- ggparcoord(qt1_6,columns = c(1,3,4,5),groupColumn = 4)
tra_g2<- ggparcoord(qt2_6,columns = c(1,3,4,5),groupColumn = 4)
tra_g3<- ggparcoord(qt3_6,columns = c(1,3,4,5),groupColumn = 4)
tra_g4<- ggparcoord(qt4_6,columns = c(1,3,4,5),groupColumn = 4)
tra_g5<- ggparcoord(qt5_6,columns = c(1,3,4,5),groupColumn = 4)
ggarrange(tra_temp, tra_g1, labels = c("Template", "Graph 1"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(tra_temp, tra_g2, labels = c("Template", "Graph 2"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(tra_temp, tra_g3, labels = c("Template", "Graph 3"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(tra_temp, tra_g4, labels = c("Template", "Graph 4"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(tra_temp, tra_g5, labels = c("Template", "Graph 5"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
```
```
```
```
```


## Procurement Channel:
```{r}
pro_temp <- ggparcoord(dt23, columns = c(1,3,4,5),groupColumn = 4,scale = "center")
pro_g1<- ggparcoord(qt1_23,columns = c(1,3,4,5), groupColumn = 4, scale = "center")
pro_g2 <- ggparcoord(qt2_23,columns = c(1,3,4,5), groupColumn = 4,scale = "center")
pro_g3 <- ggparcoord(qt3_23,columns = c(1,3,4,5), groupColumn = 4,scale = "center")
pro_g4 <- ggparcoord(qt4_23,columns = c(1,3,4,5), groupColumn = 4,scale = "center")
pro_g5 <- ggparcoord(qt5_23,columns = c(1,3,4,5), groupColumn = 4,scale = "center")
ggarrange(pro_temp, pro_g1, labels = c("Template", "Graph 1"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(pro_temp, pro_g2, labels = c("Template", "Graph 2"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(pro_temp, pro_g3, labels = c("Template", "Graph 3"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(pro_temp, pro_g4, labels = c("Template", "Graph 4"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(pro_temp, pro_g5, labels = c("Template", "Graph 5"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))

```



## Removing Source and Target:
```{r}
temp_1 <- ggparcoord(data = c(dt23), columns = c(4,5),groupColumn = 4 )
qt_1 <- ggparcoord(data = c(qt1_23), columns = c(4,5),groupColumn = 4 )
qt_2 <- ggparcoord(data = c(qt2_23), columns = c(4,5),groupColumn = 4 )
qt_3 <- ggparcoord(data = c(qt3_23), columns = c(4,5),groupColumn = 4 )
qt_4 <- ggparcoord(data = c(qt4_23), columns = c(4,5),groupColumn = 4 )
qt_5 <- ggparcoord(data = c(qt5_23), columns = c(4,5),groupColumn = 4 )
ggarrange(temp_1,qt_1,labels = c("Template", "Graph 1"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(temp_1,qt_2,labels = c("Template", "Graph 2"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(temp_1,qt_3,labels = c("Template", "Graph 3"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(temp_1,qt_4,labels = c("Template", "Graph 4"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
ggarrange(temp_1,qt_5,labels = c("Template", "Graph 5"), hjust = 0, vjust = 1, font.label = list(size = 10, color = "blue"))
```


## Network Analysis:
```{r}
# Communication Channel:
# For Template:
Sources <- dt01 %>%
  distinct(Source) %>%
  rename(label = Source)

Targets <- dt01 %>%
  distinct(Target) %>%
  rename(label = Target)

# Creating a Node List:
nodes <- full_join(Sources, Targets, by = "label")
nodes
nodes <- nodes %>% rowid_to_column("id")
nodes

# Creating an Edge List:
per_route <- dt01 %>%  
  group_by(Source, Target) %>%
  summarise(weight = n()) %>% 
  ungroup()
per_route

edges <- per_route %>% 
  left_join(nodes, by = c("Source" = "label")) %>% 
  rename(from = id)

edges <- edges %>% 
  left_join(nodes, by = c("Target" = "label")) %>% 
  rename(to = id)

edges <- select(edges, from, to, weight)
edges

# Creating a Network:
routes_network <- network(edges, vertex.attr = nodes, matrix.type = "edgelist", ignore.eval = FALSE)
class(routes_network)
routes_network


# Graph 1:
Sources_G1 <- qt1 %>%
  distinct(Source) %>%
  rename(label = Source)

Targets_G1 <- qt1 %>%
  distinct(Target) %>%
  rename(label = Target)

# Creating a Node List:
nodes_G1 <- full_join(Sources_G1, Targets_G1, by = "label")
nodes_G1
nodes_G1 <- nodes_G1 %>% rowid_to_column("id")
nodes_G1

# Creating an Edge List:
per_route_G1 <- qt1 %>%  
  group_by(Source, Target) %>%
  summarise(weight = n()) %>% 
  ungroup()
per_route_G1

edges_G1 <- per_route_G1 %>% 
  left_join(nodes_G1, by = c("Source" = "label")) %>% 
  rename(from = id)

edges_G1 <- edges_G1 %>% 
  left_join(nodes_G1, by = c("Target" = "label")) %>% 
  rename(to = id)

edges_G1 <- select(edges_G1, from, to, weight)
edges_G1

# Creating a Network:
routes_network_G1 <- network(edges_G1, vertex.attr = nodes_G1, matrix.type = "edgelist", ignore.eval = FALSE)
routes_network_G1


# Graph 2:
Sources_G2 <- qt2 %>%
  distinct(Source) %>%
  rename(label = Source)

Targets_G2 <- qt2 %>%
  distinct(Target) %>%
  rename(label = Target)

# Creating a Node List:
nodes_G2 <- full_join(Sources_G2, Targets_G2, by = "label")
nodes_G2
nodes_G2 <- nodes_G2 %>% rowid_to_column("id")
nodes_G2

# Creating an Edge List:
per_route_G2 <- qt2 %>%  
  group_by(Source, Target) %>%
  summarise(weight = n()) %>% 
  ungroup()
per_route_G2

edges_G2 <- per_route_G2 %>% 
  left_join(nodes_G2, by = c("Source" = "label")) %>% 
  rename(from = id)

edges_G2 <- edges_G2 %>% 
  left_join(nodes_G2, by = c("Target" = "label")) %>% 
  rename(to = id)

edges_G2 <- select(edges_G2, from, to, weight)
edges_G2

# Creating a Network:
routes_network_G2 <- network(edges_G2, vertex.attr = nodes_G2, matrix.type = "edgelist", ignore.eval = FALSE)
routes_network_G2


# Graph 3:
Sources_G3 <- qt3 %>%
  distinct(Source) %>%
  rename(label = Source)

Targets_G3 <- qt3 %>%
  distinct(Target) %>%
  rename(label = Target)

# Creating a Node List:
nodes_G3 <- full_join(Sources_G3, Targets_G3, by = "label")
nodes_G3
nodes_G3 <- nodes_G3 %>% rowid_to_column("id")
nodes_G3

# Creating an Edge List:
per_route_G3 <- qt3 %>%  
  group_by(Source, Target) %>%
  summarise(weight = n()) %>% 
  ungroup()
per_route_G3

edges_G3 <- per_route_G3 %>% 
  left_join(nodes_G3, by = c("Source" = "label")) %>% 
  rename(from = id)

edges_G3 <- edges_G3 %>% 
  left_join(nodes_G3, by = c("Target" = "label")) %>% 
  rename(to = id)

edges_G3 <- select(edges_G3, from, to, weight)
edges_G3

# Creating a Network:
routes_network_G3 <- network(edges_G3, vertex.attr = nodes_G3, matrix.type = "edgelist", ignore.eval = FALSE)
routes_network_G3


# Graph 4:
Sources_G4 <- qt4 %>%
  distinct(Source) %>%
  rename(label = Source)

Targets_G4 <- qt4 %>%
  distinct(Target) %>%
  rename(label = Target)

# Creating a Node List:
nodes_G4 <- full_join(Sources_G4, Targets_G4, by = "label")
nodes_G4
nodes_G4 <- nodes_G4 %>% rowid_to_column("id")
nodes_G4

# Creating an Edge List:
per_route_G4 <- qt4 %>%  
  group_by(Source, Target) %>%
  summarise(weight = n()) %>% 
  ungroup()
per_route_G4

edges_G4 <- per_route_G4 %>% 
  left_join(nodes_G4, by = c("Source" = "label")) %>% 
  rename(from = id)

edges_G4 <- edges_G4 %>% 
  left_join(nodes_G4, by = c("Target" = "label")) %>% 
  rename(to = id)

edges_G4 <- select(edges_G4, from, to, weight)
edges_G4

# Creating a Network:
routes_network_G4 <- network(edges_G4, vertex.attr = nodes_G4, matrix.type = "edgelist", ignore.eval = FALSE)
routes_network_G4


# Graph 5:
Sources_G5 <- qt5 %>%
  distinct(Source) %>%
  rename(label = Source)

Targets_G5 <- qt5 %>%
  distinct(Target) %>%
  rename(label = Target)

# Creating a Node List:
nodes_G5 <- full_join(Sources_G5, Targets_G5, by = "label")
nodes_G5
nodes_G5 <- nodes_G5 %>% rowid_to_column("id")
nodes_G5

# Creating an Edge List:
per_route_G5 <- qt5 %>%  
  group_by(Source, Target) %>%
  summarise(weight = n()) %>% 
  ungroup()
per_route_G5

edges_G5 <- per_route_G5 %>% 
  left_join(nodes_G5, by = c("Source" = "label")) %>% 
  rename(from = id)

edges_G5 <- edges_G5 %>% 
  left_join(nodes_G5, by = c("Target" = "label")) %>% 
  rename(to = id)

edges_G5 <- select(edges_G5, from, to, weight)
edges_G5

# Creating a Network:
routes_network_G5 <- network(edges_G5, vertex.attr = nodes_G5, matrix.type = "edgelist", ignore.eval = FALSE)
routes_network_G5


```


## Network Visualisation:
```{r}
plot(routes_network, vertex.cex = 3, main = "Template")
plot(routes_network_G1, vertex.cex = 3, main = "Graph 1")
plot(routes_network_G2, vertex.cex = 3, main = "Graph 2")
plot(routes_network_G3, vertex.cex = 3, main = "Graph 3")
plot(routes_network_G4, vertex.cex = 3, main = "Graph 4")
plot(routes_network_G5, vertex.cex = 3, main = "Graph 5")
```



## Interactive Network Analysis:
## VisNetwork:
```{r}
# Communication Channel:
# Weighted edges:
edges <- mutate(edges, width = weight/5 + 1)
edges_G1 <- mutate(edges_G1, width = weight/5 + 1)
edges_G2 <- mutate(edges_G2, width = weight/5 + 1)
edges_G3 <- mutate(edges_G3, width = weight/5 + 1)
edges_G4 <- mutate(edges_G4, width = weight/5 + 1)
edges_G5 <- mutate(edges_G5, width = weight/5 + 1)


# Interactive Graphs with visNetwork:
temp_com <- visNetwork(nodes, edges)%>% visIgraphLayout(layout = "layout_with_fr") %>% visEdges(arrows = "middle")
visPhysics(temp_com, stabilization = FALSE, enabled = FALSE)
g1_com <- visNetwork(nodes_G1, edges_G1)%>% visIgraphLayout(layout = "layout_with_fr") %>% visEdges(arrows = "middle")
visPhysics(g1_com, stabilization = FALSE, enabled = FALSE)
g2_com <- visNetwork(nodes_G2, edges_G2)%>% visIgraphLayout(layout = "layout_with_fr") %>% visEdges(arrows = "middle")
visPhysics(g2_com, stabilization = FALSE, enabled = FALSE)
g3_com <- visNetwork(nodes_G3, edges_G3)%>% visIgraphLayout(layout = "layout_with_fr") %>% visEdges(arrows = "middle")
visPhysics(g3_com, stabilization = FALSE, enabled = FALSE)
g4_com <- visNetwork(nodes_G4, edges_G4)%>% visIgraphLayout(layout = "layout_with_fr") %>% visEdges(arrows = "middle")
visPhysics(g4_com, stabilization = FALSE, enabled = FALSE)
g5_com <- visNetwork(nodes_G5, edges_G5)%>% visIgraphLayout(layout = "layout_with_fr") %>% visEdges(arrows = "middle")
visPhysics(g5_com, stabilization = FALSE, enabled = FALSE)

```


## Network D3.js
```{r}
# Network D3.js:
nodes_d3 <- mutate(nodes, id = id - 1)
edges_d3 <- mutate(edges, from = from - 1, to = to - 1)
forceNetwork(Links = edges_d3, Nodes = nodes_d3, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", 
             opacity = 1, fontSize = 16, zoom = TRUE)
nodes_d3_g1 <- mutate(nodes_G1, id = id - 1)
edges_d3_g1 <- mutate(edges_G1, from = from - 1, to = to - 1)
forceNetwork(Links = edges_d3_g1, Nodes = nodes_d3_g1, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", 
             opacity = 1, fontSize = 16, zoom = TRUE)
nodes_d3_g2 <- mutate(nodes_G2, id = id - 1)
edges_d3_g2 <- mutate(edges_G2, from = from - 1, to = to - 1)
forceNetwork(Links = edges_d3_g2, Nodes = nodes_d3_g2, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", 
             opacity = 1, fontSize = 16, zoom = TRUE)
nodes_d3_g3 <- mutate(nodes_G3, id = id - 1)
edges_d3_g3 <- mutate(edges_G3, from = from - 1, to = to - 1)
forceNetwork(Links = edges_d3_g3, Nodes = nodes_d3_g3, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", 
             opacity = 1, fontSize = 16, zoom = TRUE)
nodes_d3_g4 <- mutate(nodes_G4, id = id - 1)
edges_d3_g4 <- mutate(edges_G4, from = from - 1, to = to - 1)
forceNetwork(Links = edges_d3_g4, Nodes = nodes_d3_g4, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", 
             opacity = 1, fontSize = 16, zoom = TRUE)
nodes_d3_g5 <- mutate(nodes_G5, id = id - 1)
edges_d3_g5 <- mutate(edges_G5, from = from - 1, to = to - 1)
forceNetwork(Links = edges_d3_g5, Nodes = nodes_d3_g5, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", 
             opacity = 1, fontSize = 16, zoom = TRUE)
```



## Skankey Network:
```{r}
sankeyNetwork(Links = edges_d3, Nodes = nodes_d3, Source = "from", Target = "to", 
              NodeID = "label", Value = "weight", fontSize = 16, unit = "Node(s)")
sankeyNetwork(Links = edges_d3_g1, Nodes = nodes_d3_g1, Source = "from", Target = "to", 
              NodeID = "label", Value = "weight", fontSize = 16, unit = "Node(s)")
sankeyNetwork(Links = edges_d3_g2, Nodes = nodes_d3_g2, Source = "from", Target = "to", 
              NodeID = "label", Value = "weight", fontSize = 16, unit = "Node(s)")
sankeyNetwork(Links = edges_d3_g3, Nodes = nodes_d3_g3, Source = "from", Target = "to", 
              NodeID = "label", Value = "weight", fontSize = 16, unit = "Node(s)")
sankeyNetwork(Links = edges_d3_g4, Nodes = nodes_d3_g4, Source = "from", Target = "to", 
              NodeID = "label", Value = "weight", fontSize = 16, unit = "Node(s)")
sankeyNetwork(Links = edges_d3_g4, Nodes = nodes_d3_g4, Source = "from", Target = "to", 
              NodeID = "label", Value = "weight", fontSize = 16, unit = "Node(s)")



```

```{r}
proc_s1_full <- data.table::fread(here::here("dataQ3","FinalGraphs2", "dfProcSeed1-Graph2ReducedFinal.csv"))
proc_s3_full <- data.table::fread(here::here("dataQ3","FinalGraphs2", "dfProcSeed3-Graph2ReducedFinal.csv"))
```

## Proc Seed 1:

```{r}
Sources1 <- proc_s1_full %>%
  distinct(Source) %>%
  rename(label = Source)

Targets1 <- proc_s1_full %>%
  distinct(Target) %>%
  rename(label = Target)

# Creating a Node List:
nodes1 <- full_join(Sources1, Targets1, by = "label")
nodes1
nodes1 <- nodes1 %>% rowid_to_column("id")
nodes1

# Creating an Edge List:
per_route1 <- proc_s1_full %>%  
  group_by(Source, Target) %>%
  summarise(weight = n()) %>% 
  ungroup()
per_route1

edges1 <- per_route1 %>% 
  left_join(nodes1, by = c("Source" = "label")) %>% 
  rename(from = id)

edges1 <- edges1 %>% 
  left_join(nodes1, by = c("Target" = "label")) %>% 
  rename(to = id)

edges1 <- select(edges1, from, to, weight)
edges1

# Creating a Network:
routes_network1 <- network(edges1, vertex.attr = nodes1, matrix.type = "edgelist", ignore.eval = FALSE)
class(routes_network1)
routes_network1

```

## Proc Seed 3:
```{r}
Sources <- proc_s3_full %>%
  distinct(Source) %>%
  rename(label = Source)

Targets <- proc_s3_full %>%
  distinct(Target) %>%
  rename(label = Target)

# Creating a Node List:
nodes <- full_join(Sources, Targets, by = "label")
nodes
nodes <- nodes %>% rowid_to_column("id")
nodes

# Creating an Edge List:
per_route <- proc_s3_full %>%  
  group_by(Source, Target) %>%
  summarise(weight = n()) %>% 
  ungroup()
per_route

edges <- per_route %>% 
  left_join(nodes, by = c("Source" = "label")) %>% 
  rename(from = id)

edges <- edges %>% 
  left_join(nodes, by = c("Target" = "label")) %>% 
  rename(to = id)

edges <- select(edges, from, to, weight)
edges

# Creating a Network:
routes_network <- network(edges, vertex.attr = nodes, matrix.type = "edgelist", ignore.eval = FALSE)
class(routes_network)
routes_network
```


## Network D3:
## Reduced:

```{r}
Graph_Attributes <- data.table::fread(here::here("data", "CGCS-GraphData-NodeTypes.csv"))
node_types <- unique(Graph_Attributes$NodeType)
arr1 <- array()
for(node in nodes1$label){
  
    #arr <- append(c(arr), c(Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType))
  arr1 <- rbind(arr1, Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType)
  
  
}
arr1[2:111]

## Proc seed 1:
nodes_g1 <- mutate(nodes1, id = arr1[2:111])
edges_g1 <- mutate(edges1, from = from - 1, to = to - 1)
q3g1 <- forceNetwork(Links = edges_g1, Nodes = nodes_g1, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", linkDistance = 200,
             opacity = 1, fontSize = 16, zoom = TRUE)

saveNetwork(q3g1, file = "q3g1.html")

arr <- array()
for(node in nodes$label){
  
    #arr <- append(c(arr), c(Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType))
  arr <- rbind(arr, Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType)
  
  
}
## Proc seed 3:
nodes_g3 <- mutate(nodes, id = arr[2:85])
edges_g3 <- mutate(edges, from = from - 1, to = to - 1)
q3g2 <- forceNetwork(Links = edges_g3, Nodes = nodes_g3, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", linkDistance = 200,
             opacity = 1, fontSize = 16, zoom = TRUE)

saveNetwork(q3g2, file = "q3g2.html")

```

## Level 1 and 2 Seed1:

```{r}
proc_s1_l1 <- data.table::fread(here::here("dataQ3","InitialGraphs", "dfProcSeed1_Lvl1.csv"))
proc_s1_l2 <- data.table::fread(here::here("dataQ3","InitialGraphs", "dfProcSeed1_Lvl2.csv"))
proc_s1 <- data.table::fread(here::here("dataQ3","InitialGraphs", "dfProcSeed1-Graph2Full.csv"))


```

```{r}
Sources <- proc_s1_l1 %>%
  distinct(Source) %>%
  rename(label = Source)

Targets <- proc_s1_l1 %>%
  distinct(Target) %>%
  rename(label = Target)

# Creating a Node List:
nodes <- full_join(Sources, Targets, by = "label")
nodes
nodes <- nodes %>% rowid_to_column("id")
nodes

# Creating an Edge List:
per_route <- proc_s1_l1 %>%  
  group_by(Source, Target) %>%
  summarise(weight = n()) %>% 
  ungroup()
per_route

edges <- per_route %>% 
  left_join(nodes, by = c("Source" = "label")) %>% 
  rename(from = id)

edges <- edges %>% 
  left_join(nodes, by = c("Target" = "label")) %>% 
  rename(to = id)

edges <- select(edges, from, to, weight)
edges

# Creating a Network:
routes_network <- network(edges, vertex.attr = nodes, matrix.type = "edgelist", ignore.eval = FALSE)
class(routes_network)
routes_network
```

```{r}
arr <- array()
for(node in nodes$label){
  
    #arr <- append(c(arr), c(Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType))
  arr <- rbind(arr, Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType)
  
  
}
## Proc seed 3:
nodes_g3 <- mutate(nodes, id = arr[2:4])
edges_g3 <- mutate(edges, from = from - 1, to = to - 1)
q3g1L1 <- forceNetwork(Links = edges_g3, Nodes = nodes_g3, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", linkDistance = 200,
             opacity = 1, fontSize = 16, zoom = TRUE, legend = TRUE)

saveNetwork(q3g1L1, file = "q3g1L1.html")
```

```{r}
Sources <- proc_s1_l2 %>%
  distinct(Source) %>%
  rename(label = Source)

Targets <- proc_s1_l2 %>%
  distinct(Target) %>%
  rename(label = Target)

# Creating a Node List:
nodes <- full_join(Sources, Targets, by = "label")
nodes
nodes <- nodes %>% rowid_to_column("id")
nodes

# Creating an Edge List:
per_route <- proc_s1_l2 %>%  
  group_by(Source, Target) %>%
  summarise(weight = n()) %>% 
  ungroup()
per_route

edges <- per_route %>% 
  left_join(nodes, by = c("Source" = "label")) %>% 
  rename(from = id)

edges <- edges %>% 
  left_join(nodes, by = c("Target" = "label")) %>% 
  rename(to = id)

edges <- select(edges, from, to, weight)
edges

# Creating a Network:
routes_network <- network(edges, vertex.attr = nodes, matrix.type = "edgelist", ignore.eval = FALSE)
class(routes_network)
routes_network

arr <- array()
for(node in nodes$label){
  
    #arr <- append(c(arr), c(Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType))
  arr <- rbind(arr, Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType)
  
  
}
## Proc seed 1:
nodes_g3 <- mutate(nodes, id = arr[2:10050])
edges_g3 <- mutate(edges, from = from - 1, to = to - 1)
q3g1L2 <- forceNetwork(Links = edges_g3, Nodes = nodes_g3, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", linkDistance = 300,
             opacity = 1, fontSize = 16, zoom = TRUE, legend = TRUE)

saveNetwork(q3g1L2, file = "q3g1L2.html")
```

## Extended Network Seed 1:

```{r}
Sources <- proc_s1 %>%
  distinct(Source) %>%
  rename(label = Source)

Targets <- proc_s1 %>%
  distinct(Target) %>%
  rename(label = Target)

# Creating a Node List:
nodes <- full_join(Sources, Targets, by = "label")
nodes
nodes <- nodes %>% rowid_to_column("id")
nodes

# Creating an Edge List:
per_route <- proc_s1 %>%  
  group_by(Source, Target) %>%
  summarise(weight = n()) %>% 
  ungroup()
per_route

edges <- per_route %>% 
  left_join(nodes, by = c("Source" = "label")) %>% 
  rename(from = id)

edges <- edges %>% 
  left_join(nodes, by = c("Target" = "label")) %>% 
  rename(to = id)

edges <- select(edges, from, to, weight)
edges

# Creating a Network:
routes_network <- network(edges, vertex.attr = nodes, matrix.type = "edgelist", ignore.eval = FALSE)
class(routes_network)
routes_network

arr <- array()
for(node in nodes$label){
  
    #arr <- append(c(arr), c(Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType))
  arr <- rbind(arr, Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType)
  
  
}
## Proc seed 3:
nodes_g3 <- mutate(nodes, id = arr[2:111])
edges_g3 <- mutate(edges, from = from - 1, to = to - 1)
q3g1full <- forceNetwork(Links = edges_g3, Nodes = nodes_g3, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", linkDistance = 300,
             opacity = 1, fontSize = 16, zoom = TRUE, legend = TRUE)

saveNetwork(q3g1full, file = "q3g1full.html")
```


## Proc Seed 3:
## 
```{r}
proc_s3_red <- data.table::fread(here::here("dataQ3","FinalGraphs2", "dfProcSeed3-Graph2ReducedFinal.csv"))
proc_s3_l1 <- data.table::fread(here::here("dataQ3","InitialGraphs", "dfProcSeed3_Lvl1.csv"))
proc_s3_l2 <- data.table::fread(here::here("dataQ3","InitialGraphs", "dfProcSeed3_Lvl2.csv"))
proc_s3 <- data.table::fread(here::here("dataQ3","InitialGraphs", "dfProcSeed3-Graph2Full.csv"))
```

## Reduced:

```{r}
Sources <- proc_s3_red %>%
  distinct(Source) %>%
  rename(label = Source)

Targets <- proc_s3_red %>%
  distinct(Target) %>%
  rename(label = Target)

# Creating a Node List:
nodes <- full_join(Sources, Targets, by = "label")
nodes
nodes <- nodes %>% rowid_to_column("id")
nodes

# Creating an Edge List:
per_route <- proc_s3_red %>%  
  group_by(Source, Target) %>%
  summarise(weight = n()) %>% 
  ungroup()
per_route

edges <- per_route %>% 
  left_join(nodes, by = c("Source" = "label")) %>% 
  rename(from = id)

edges <- edges %>% 
  left_join(nodes, by = c("Target" = "label")) %>% 
  rename(to = id)

edges <- select(edges, from, to, weight)
edges

# Creating a Network:
routes_network <- network(edges, vertex.attr = nodes, matrix.type = "edgelist", ignore.eval = FALSE)
class(routes_network)
routes_network

arr <- array()
for(node in nodes$label){
  
    #arr <- append(c(arr), c(Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType))
  arr <- rbind(arr, Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType)
  
  
}
## Proc seed 3:
nodes_g3 <- mutate(nodes, id = arr[2:85])
edges_g3 <- mutate(edges, from = from - 1, to = to - 1)
q3g2red <- forceNetwork(Links = edges_g3, Nodes = nodes_g3, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", linkDistance = 300,
             opacity = 1, fontSize = 16, zoom = TRUE, legend = TRUE)

saveNetwork(q3g2red, file = "q3g2.html")
```
```{r}
## Level 1:
Sources <- proc_s3_l1 %>%
  distinct(Source) %>%
  rename(label = Source)

Targets <- proc_s3_l1 %>%
  distinct(Target) %>%
  rename(label = Target)

# Creating a Node List:
nodes <- full_join(Sources, Targets, by = "label")
nodes
nodes <- nodes %>% rowid_to_column("id")
nodes

# Creating an Edge List:
per_route <- proc_s3_l1 %>%  
  group_by(Source, Target) %>%
  summarise(weight = n()) %>% 
  ungroup()
per_route

edges <- per_route %>% 
  left_join(nodes, by = c("Source" = "label")) %>% 
  rename(from = id)

edges <- edges %>% 
  left_join(nodes, by = c("Target" = "label")) %>% 
  rename(to = id)

edges <- select(edges, from, to, weight)
edges

# Creating a Network:
routes_network <- network(edges, vertex.attr = nodes, matrix.type = "edgelist", ignore.eval = FALSE)
class(routes_network)
routes_network

arr <- array()
for(node in nodes$label){
  
    #arr <- append(c(arr), c(Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType))
  arr <- rbind(arr, Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType)
  
  
}
## Proc seed 3:
nodes_g3 <- mutate(nodes, id = arr[2:4])
edges_g3 <- mutate(edges, from = from - 1, to = to - 1)
q3g2L1 <- forceNetwork(Links = edges_g3, Nodes = nodes_g3, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", linkDistance = 300,
             opacity = 1, fontSize = 16, zoom = TRUE, legend = TRUE)

saveNetwork(q3g2L1, file = "q3g2L1.html")
```

## Level 2:

```{r}
Sources <- proc_s3_l2 %>%
  distinct(Source) %>%
  rename(label = Source)

Targets <- proc_s3_l2 %>%
  distinct(Target) %>%
  rename(label = Target)

# Creating a Node List:
nodes <- full_join(Sources, Targets, by = "label")
nodes
nodes <- nodes %>% rowid_to_column("id")
nodes

# Creating an Edge List:
per_route <- proc_s3_l2 %>%  
  group_by(Source, Target) %>%
  summarise(weight = n()) %>% 
  ungroup()
per_route

edges <- per_route %>% 
  left_join(nodes, by = c("Source" = "label")) %>% 
  rename(from = id)

edges <- edges %>% 
  left_join(nodes, by = c("Target" = "label")) %>% 
  rename(to = id)

edges <- select(edges, from, to, weight)
edges

# Creating a Network:
routes_network <- network(edges, vertex.attr = nodes, matrix.type = "edgelist", ignore.eval = FALSE)
class(routes_network)
routes_network

arr <- array()
for(node in nodes$label){
  
    #arr <- append(c(arr), c(Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType))
  arr <- rbind(arr, Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType)
  
  
}
## Proc seed 3:
nodes_g3 <- mutate(nodes, id = arr[2:5186])
edges_g3 <- mutate(edges, from = from - 1, to = to - 1)
q3g2L2 <- forceNetwork(Links = edges_g3, Nodes = nodes_g3, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", linkDistance = 300,
             opacity = 1, fontSize = 16, zoom = TRUE, legend = TRUE)

saveNetwork(q3g2L2, file = "q3g2L2.html")
```

## Extended:

```{r}
Sources <- proc_s3 %>%
  distinct(Source) %>%
  rename(label = Source)

Targets <- proc_s3 %>%
  distinct(Target) %>%
  rename(label = Target)

# Creating a Node List:
nodes <- full_join(Sources, Targets, by = "label")
nodes
nodes <- nodes %>% rowid_to_column("id")
nodes

# Creating an Edge List:
per_route <- proc_s3 %>%  
  group_by(Source, Target) %>%
  summarise(weight = n()) %>% 
  ungroup()
per_route

edges <- per_route %>% 
  left_join(nodes, by = c("Source" = "label")) %>% 
  rename(from = id)

edges <- edges %>% 
  left_join(nodes, by = c("Target" = "label")) %>% 
  rename(to = id)

edges <- select(edges, from, to, weight)
edges

# Creating a Network:
routes_network <- network(edges, vertex.attr = nodes, matrix.type = "edgelist", ignore.eval = FALSE)
class(routes_network)
routes_network

arr <- array()
for(node in nodes$label){
  
    #arr <- append(c(arr), c(Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType))
  arr <- rbind(arr, Graph_Attributes[Graph_Attributes$NodeID==node]$NodeType)
  
  
}
## Proc seed 3:
nodes_g3 <- mutate(nodes, id = arr[2:85])
edges_g3 <- mutate(edges, from = from - 1, to = to - 1)
q3g2full <- forceNetwork(Links = edges_g3, Nodes = nodes_g3, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", linkDistance = 300,
             opacity = 1, fontSize = 16, zoom = TRUE, legend = TRUE)

saveNetwork(q3g2full, file = "q3g2full.html")
```

